The framing of active school travel in Ontario, Canada as a health and built environment issue

### 2022-01-27 AST-Framing-Ontario/AST-Framing-Ontario.tex

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={The framing of active school travel in Ontario, Canada as a health and built environment issue},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

In response to this trend, the Government of Ontario, in Canada, created
a fund in 2017 to support communities across the province in developing
AST initiatives. Green Communities Canada runs the program, called
\emph{Ontario Active School Travel}, and determines the projects that
will be funded with their support (Canada, 2020a). As of December 2021,
OAST has awarded over 2 million Canadian dollars and provided resources
for over 25 projects across Ontario. Many communities implemented school
travel planning (STP), along with encouragement activities like walking
school buses or developed resources for schools and parents, among other
actions (see Canada, 2020b). In this context, STP is a popular
``school-specific'' intervention led by a facilitator that brings
together a committee of stakeholders from diverse sectors including
education, planning, transportation, and public health to develop action
plans (Buliung et al., 2011; Mammen, M. R. Stone, Ron Buliung, et al.,
2014). The five-step process involves identifying barriers to AST based
on the local context and implementing approaches or activities following
the 5 E's that alleviate concerns about AST and make AST safer and more
convenient (Buliung et al., 2011; Lang et al., 2011).

@@

In this paper, we use text mining and topic modelling to examine how
three STP stakeholder groups in Ontario (i.e., municipalities, school
boards, and transportation consortia) frame the issue of AST. We
assembled a corpus of texts from webpages that can be considered an
important source of information for the general public or parents who
are interested in AST. We examine word frequency, bigrams, and
concordances in these selected documents, and also identify key topics
presented by each stakeholder group. We then compare the findings from
these documents to a selection of studies on AST and explore the extent
to which there is concordance between the literature on AST and
materials shared with the public.

@@

Factors that influence AST have been presented and organized using a
socio-ecological model (SEM) (Mitra, 2013) or systems model (Badland et
al., 2016) whereby children's travel behaviour is understood within the
context of their household, social, neighbourhood, and policy
environments. Individual characteristics of the child are also
determinants. The SEM comes from the field of public health and is a
useful framework for understanding complex health behaviours, including
travel habits such as walking or bicycling to school, because it
identifies multiple determinants that need to be addressed by
interventions to facilitate behaviour change. The consensus in the
literature is that various factors are interrelated and that
interventions should target multiple levels in order to increase levels
of healthy and physically active modes of travel to school (Mitra,
2013). Rather than describing an extensive list of factors that
influence AST and mode choice in Canada, which has been covered
elsewhere (e.g., Mammen et al., 2012; Mitra, 2013; Rothman et al., 2018;
Wilson et al., 2018), we briefly discuss a few potentially modifiable
determinants that may be targeted for change through STP.

@@

The ``central organizing idea or story line'' of AST, to apply the
definition from Gamson and Modigliani (1987), could also affect broader
support in the community. Municipal representatives are perceived to be
instrumental but the involvement of other stakeholder groups (e.g.,
busing consortium representatives and local residents) can be lacking
(Buttazzoni et al., 2018). In Ontario, it would be reasonable to say
that AST has become a policy issue on the education and public health
agendas over this time as evidenced by the financial contribution from
the provincial government. The support from a range of municipal
representatives (see Buttazzoni et al., 2018; Mammen et al., 2015)
demonstrates that the ``policy stream'' (see Kingdon, 1984) has been
well engaged. It is unknown to what degree the general public (i.e.,
local residents) has been exposed to messaging about AST, which could
affect their participation in the STP process as desired by STP
facilitators (Buttazzoni et al., 2018).

The success of STP interventions would likely depend on parental
judgments of factors that are related to school travel, as well as
support from key policy makers. For example, parents have been found to
view mixed land use as conducive for driving, despite transport planners
viewing neighbourhoods with mixed uses as key for encouraging more
active travel (Buliung et al., 2021). Therefore, stakeholder groups
involved in STP must make important choices about the proposed solutions
and potential benefits that ought to be communicated to parents and the
general public about AST to convey its importance as a policy issue and
to facilitate adoption of AST. Publicly available content about AST,
therefore, needs to effectively engage multiple audiences on this policy
issue including parents, children, politicians, and school
representatives. This information should reflect current knowledge from
research on school travel, plus content specific to local factors that
influence AST, so that the challenges of AST are adequately defined and
the opportunities or solutions to address the problems are clear.
However, it is unknown to what degree STP materials presented to the
general public reflect the scope of evidence from the literature on AST.

@@

\cellcolor{gray!6}{active} & \cellcolor{gray!6}{248} & \cellcolor{gray!6}{26} & \cellcolor{gray!6}{active} & \cellcolor{gray!6}{124} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{active} & \cellcolor{gray!6}{67} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{walking} & \cellcolor{gray!6}{5137} & \cellcolor{gray!6}{222}\\
travel & 126 & 20 & bus & 120 & 20 & walking & 55 & 8 & parents & 3946 & 211\\
\cellcolor{gray!6}{walking} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{travel} & \cellcolor{gray!6}{103} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{49} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{distance} & \cellcolor{gray!6}{3271} & \cellcolor{gray!6}{205}\\
bike & 87 & 15 & information & 65 & 21 & travel & 41 & 8 & students & 2960 & 173\\
\cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{78} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{walking} & \cellcolor{gray!6}{57} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{students} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{2753} & \cellcolor{gray!6}{171}\\

@@

safety & 71 & 21 & walk & 53 & 13 & safety & 32 & 6 & environment & 2631 & 202\\
\cellcolor{gray!6}{health} & \cellcolor{gray!6}{65} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{weather} & \cellcolor{gray!6}{40} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{help} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{activity} & \cellcolor{gray!6}{2371} & \cellcolor{gray!6}{209}\\
physical & 63 & 18 & safety & 40 & 19 & schools & 25 & 9 & traffic & 2353 & 208\\
\cellcolor{gray!6}{traffic} & \cellcolor{gray!6}{59} & \cellcolor{gray!6}{20} & \cellcolor{gray!6}{safe} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{children} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{choice} & \cellcolor{gray!6}{2299} & \cellcolor{gray!6}{169}\\
road & 56 & 13 & services & 37 & 17 & community & 24 & 7 & physical & 2256 & 215\\

@@

\cellcolor{gray!6}{activity} & \cellcolor{gray!6}{55} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{planning} & \cellcolor{gray!6}{37} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{bus} & \cellcolor{gray!6}{18} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{trips} & \cellcolor{gray!6}{2194} & \cellcolor{gray!6}{170}\\
schools & 52 & 14 & parents & 32 & 17 & route & 17 & 5 & car & 2148 & 195\\
\cellcolor{gray!6}{children} & \cellcolor{gray!6}{47} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{sustainable} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{zone} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{safety} & \cellcolor{gray!6}{2140} & \cellcolor{gray!6}{204}\\
plan & 45 & 16 & children & 31 & 14 & resources & 16 & 6 & time & 2101 & 218\\
\cellcolor{gray!6}{students} & \cellcolor{gray!6}{44} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{child} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{day} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{factors} & \cellcolor{gray!6}{2101} & \cellcolor{gray!6}{216}\\

@@

walk & 43 & 18 & day & 29 & 13 & safe & 15 & 5 & child & 2085 & 187\\
\cellcolor{gray!6}{public} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{routes} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{planning} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{2008} & \cellcolor{gray!6}{200}\\
community & 37 & 19 & physical & 28 & 11 & physical & 15 & 7 & public & 1983 & 208\\
\cellcolor{gray!6}{safe} & \cellcolor{gray!6}{34} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{health} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{healthy} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{age} & \cellcolor{gray!6}{1783} & \cellcolor{gray!6}{211}\\
benefits & 32 & 17 & inclement & 25 & 11 & traffic & 13 & 6 & urban & 1768 & 200\\

@@

\cellcolor{gray!6}{play} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{eligibility} & \cellcolor{gray!6}{24} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{support} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{home} & \cellcolor{gray!6}{1715} & \cellcolor{gray!6}{199}\\
resources & 30 & 13 & consortium & 24 & 9 & families & 13 & 5 & social & 1713 & 191\\
\cellcolor{gray!6}{healthy} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{region} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{way} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{different} & \cellcolor{gray!6}{1713} & \cellcolor{gray!6}{215}\\
routes & 27 & 13 & service & 22 & 11 & student & 12 & 5 & mobility & 1659 & 138\\
\cellcolor{gray!6}{lanes} & \cellcolor{gray!6}{26} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{•} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{region} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{significant} & \cellcolor{gray!6}{1650} & \cellcolor{gray!6}{208}\\

@@

\begin{verbatim}
## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
## "none")` instead.
\end{verbatim}

\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-1.pdf}

\begin{verbatim}
## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
## "none")` instead.
\end{verbatim}

\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-2.pdf}

\begin{verbatim}
## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
## "none")` instead.
\end{verbatim}

\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-3.pdf}

\begin{verbatim}
## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
## "none")` instead.
\end{verbatim}

\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-4.pdf}

\begin{verbatim}
## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
## "none")` instead.
\end{verbatim}

\includegraphics{AST-Framing-Ontario_files/figure-latex/evaluate-lda-5.pdf}

@@

Using topic modelling, we analyzed how AST is framed in documents
available to the general public on the websites of STP stakeholder
groups in Ontario. We found that AST is primarily framed to parents as
beneficial to the health and wellbeing of children and to environmental
sustainability. This was confirmed by the most common bigrams identified
in the policy corpus, as well as the topics identified by the LDA model.
The policy documents adequately reflect the evidence that AST
contributes positively to children's physical health (see Faulkner et
al., 2009; Schoeppe et al., 2015), although the statements regarding the
benefits of AST to children's school performance and cognitive
development need to be studied further to produce stronger evidence
({\textbf{???}}). STP stakeholder groups also communicate that
increasing AST may reduce traffic near and around schools. This
presumably is communicated to alleviate parental concerns about traffic
and safety (Evers et al., 2014; Mammen et al., 2012; Rothman et al.,
2015; Wilson et al., 2018) or reduce the frequency of risky behaviours
from drivers around schools (Rothman et al., 2017). However, the
documents do not explain why declining rates of AST are a problem for
the particular community or convey any urgency to this issue so that it
attracts the attention of parents, the general public, or policy makers.
Communicating the potential outcomes of increased AST may be persuasive
arguments to motivate behaviour change, but these documents do not
appear to encourage parents or the general public to view their
behaviour as problematic or unhealthy for their children's development.
For example, Canadian parents who escort their children to school have
reported concerns about traffic volume around schools (Mammen et al.,
2012), but may not recognize that their own behaviour contributes to the
problem that is perceived to prevent their child from safely walking or
bicycling to school (Collins and Kearns, 2001).

@@

Given the range of factors that influence AST in a Canadian setting
(\emph{inter alia}, see Mammen et al., 2012; Mitra, 2013; Rothman et
al., 2018; Wilson et al., 2018), STP stakeholder groups must decide
which points of intervention that they can reasonably have some
influence towards. This would also depend on the local context to ensure
that barriers to AST as perceived by parents are addressed. It could be
that STP stakeholder groups perceive to have more control over
micro-scale elements of the built environment, like traffic calming
measures or speed limits, rather ``non-modifiable'' factors like street
density or land use mix. It would certainly be much more difficult for
STP stakeholder groups to influence the number of trips to different
destinations that households need to make or to intervene in residential
location, which affects distance to school. A focus on changing parental
perceptions is recommended by many scholars since parents are the
``gatekeeper'' for children's mobility, but the information communicated
by STP stakeholder groups in Ontario should reflect a broader range of
factors that influence AST.

@@

There is also a noticeable lack of focus on individual and interpersonal
determinants of AST in the policy documents. For example, the role of
convenience and inclement weather in shaping household travel decisions
(Buliung et al., 2011) or the age at which children become allowed to
travel by active modes or independently (Mammen et al., 2012) were not
discussed. The desire to escort children to school, which has been noted
by parents as a reason to continue driving (Westman, Friman, et al.,
2017), is also not adequately addressed by STP stakeholder groups. The
complexity of travel arrangements that must be coordinated by households
(see Buliung et al., 2021) and the dominant parenting culture to protect
children from risk ({\textbf{???}}) are likewise overlooked. STP
stakeholders may wish to emphasize to parents that older children have
greater traffic safety and cognitive abilities to navigate their own
routes to school, which could encourage parents to develop their
child(ren)'s travel skills over time. Additional attention should be
paid to the reasons why parents perceive driving to be more convenient.

@@

Although the ``policy stream'' appears to have been adequately engaged
in Ontario communities, it could be that the decline of AST has not been
sufficiently framed as ``problematic'' to warrant more widespread
awareness or solutions. If Canadian STP stakeholder groups wish to
involve more local residents in their efforts (Buttazzoni et al., 2018),
it would also be worthwhile for them to produce different material that
communicates why this issue is important to the general public,
regardless of whether they currently have children commuting to/from
school. The ``political steam'' could also be further engaged by working
with advocacy groups who could attract more support from a broader
coalition of individuals.

@@

\leavevmode\hypertarget{ref-romeroChildrenExperiencesEnjoyment2015}{}%
Romero, V., 2015. Children׳s experiences: Enjoyment and fun as
additional encouragement for walking to school. Journal of Transport \&
Health 2, 230--237.
doi:\href{https://doi.org/10.1016/j.jth.2015.01.002}{10.1016/j.jth.2015.01.002}

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={The framing of active school travel in Ontario, Canada as a health and built environment issue},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

In response to this trend, the Government of Ontario, in Canada, created
a fund in 2017 to support communities across the province in developing
AST initiatives. Green Communities Canada runs the program, called
\emph{Ontario Active School Travel}, and determines the projects that
will be funded with their support (Canada, 2020a). As of December 2021,
OAST has awarded over 2 million Canadian dollars and provided resources
to over 25 projects across Ontario. Many communities implemented school
travel planning (STP), along with encouragement activities like walking
school buses or developed resources for schools and parents, among other
actions (see Canada, 2020b). In this context, STP is a popular
``school-specific'' intervention led by a facilitator that brings
together a committee of stakeholders from diverse sectors including
education, planning, transportation, and public health to develop action
plans (Buliung et al., 2011; Mammen, M. R. Stone, Ron Buliung, et al.,
2014). The five-step process involves identifying barriers to AST based
on the local context and implementing approaches or activities following
the 5 E's that alleviate concerns about AST and make AST safer and more
convenient (Buliung et al., 2011; Lang et al., 2011).

@@

In this paper, we use natural language processing to examine how three
STP stakeholder groups in Ontario (i.e., municipalities, school boards,
and transportation consortia) frame the issue of AST. We assembled a
corpus of texts from webpages that can be considered an important source
of information for the general public or parents who are interested in
AST. We examine word frequency, bigrams, and concordances in these
selected documents, and also identify key topics presented by each
stakeholder group. We then compare the findings from these documents to
a selection of studies on AST and explore the extent to which there is
concordance between the literature on AST and materials shared with the
public.

@@

Factors that influence AST have been presented and organized using a
socio-ecological model (SEM) (Mitra, 2013) or systems model (Badland et
al., 2016) whereby children's travel behaviour is understood within the
context of their household, social, neighbourhood, and policy
environments. Individual characteristics of the child are also
determinants. The SEM comes from the field of public health and is a
useful framework for understanding complex health behaviours, including
travel habits such as walking or bicycling to school, because it
identifies multiple determinants that need to be addressed by
interventions to facilitate behaviour change. The consensus in the
literature is that various factors are interrelated and that
interventions should target multiple levels in order to increase levels
of healthy and physically active modes of travel to school (Mitra,
2013). Rather than describing an extensive list of factors that
influence AST and mode choice in Canada (e.g., Mammen et al., 2012;
Mitra, 2013; Rothman et al., 2018; Wilson et al., 2018), we discuss a
few potentially modifiable determinants that may be targeted for change
through STP.

@@

The ``central organizing idea or story line'' of AST, to apply the
definition from Gamson and Modigliani (1987), could also affect broader
support in the community. Municipal representatives are perceived to be
instrumental but the involvement of other stakeholder groups (e.g.,
busing consortium representatives and local residents) can be lacking
(Buttazzoni et al., 2018). In Ontario, it would be reasonable to say
that AST has become a policy issue on the education and public health
agendas over this time as evidenced by the financial contribution from
the provincial government. The support from a range of municipal
representatives (see Buttazzoni et al., 2018; Mammen et al., 2015)
demonstrates that the ``policy stream'' (see Kingdon, 1984) has been
well engaged. However, it is unknown to what degree the general public
(i.e., local residents) has been exposed to messaging about AST, or how
they view the AST issue, which could affect their participation in the
STP process as desired by STP facilitators (Buttazzoni et al., 2018).

The success of STP interventions would likely depend on parental
judgments of factors that are related to school travel, as well as
support from key policy makers. For example, parents have been found to
view mixed land use as conducive for driving, despite transport planners
viewing neighbourhoods with mixed uses as key for encouraging more
active travel (Buliung et al., 2021). Therefore, stakeholder groups
involved in STP must make important choices about the proposed solutions
and potential benefits of AST that ought to be communicated to parents
and the general public to convey its importance as a policy issue and to
facilitate adoption of AST. Publicly available content about AST,
therefore, needs to effectively engage multiple audiences on this policy
issue including parents, children, politicians, and school
representatives. This information should reflect current knowledge from
research on school travel, plus content specific to local factors that
influence AST, so that the challenges of AST are adequately defined and
the opportunities or solutions to address the problems are clear.
However, it is unknown to what degree STP materials presented to the
general public reflect the scope of evidence from the literature on AST.

@@

\cellcolor{gray!6}{active} & \cellcolor{gray!6}{248} & \cellcolor{gray!6}{26} & \cellcolor{gray!6}{active} & \cellcolor{gray!6}{124} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{active} & \cellcolor{gray!6}{67} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{walking} & \cellcolor{gray!6}{5059} & \cellcolor{gray!6}{220}\\
travel & 126 & 20 & bus & 120 & 20 & walking & 55 & 8 & parents & 3927 & 209\\
\cellcolor{gray!6}{walking} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{travel} & \cellcolor{gray!6}{103} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{49} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{distance} & \cellcolor{gray!6}{3252} & \cellcolor{gray!6}{203}\\
bike & 87 & 15 & information & 65 & 21 & travel & 41 & 8 & students & 2956 & 171\\
\cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{78} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{walking} & \cellcolor{gray!6}{57} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{students} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{cycling} & \cellcolor{gray!6}{2739} & \cellcolor{gray!6}{170}\\

@@

safety & 71 & 21 & walk & 53 & 13 & safety & 32 & 6 & environment & 2585 & 200\\
\cellcolor{gray!6}{health} & \cellcolor{gray!6}{65} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{weather} & \cellcolor{gray!6}{40} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{help} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{traffic} & \cellcolor{gray!6}{2334} & \cellcolor{gray!6}{206}\\
physical & 63 & 18 & safety & 40 & 19 & schools & 25 & 9 & choice & 2295 & 167\\
\cellcolor{gray!6}{traffic} & \cellcolor{gray!6}{59} & \cellcolor{gray!6}{20} & \cellcolor{gray!6}{safe} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{children} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{activity} & \cellcolor{gray!6}{2265} & \cellcolor{gray!6}{207}\\
road & 56 & 13 & services & 37 & 17 & community & 24 & 7 & physical & 2238 & 213\\

@@

\cellcolor{gray!6}{activity} & \cellcolor{gray!6}{55} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{planning} & \cellcolor{gray!6}{37} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{bus} & \cellcolor{gray!6}{18} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{trips} & \cellcolor{gray!6}{2164} & \cellcolor{gray!6}{168}\\
schools & 52 & 14 & parents & 32 & 17 & route & 17 & 5 & car & 2140 & 193\\
\cellcolor{gray!6}{children} & \cellcolor{gray!6}{47} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{sustainable} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{8} & \cellcolor{gray!6}{zone} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{safety} & \cellcolor{gray!6}{2111} & \cellcolor{gray!6}{202}\\
plan & 45 & 16 & children & 31 & 14 & resources & 16 & 6 & time & 2091 & 216\\
\cellcolor{gray!6}{students} & \cellcolor{gray!6}{44} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{child} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{day} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{factors} & \cellcolor{gray!6}{2083} & \cellcolor{gray!6}{214}\\

@@

walk & 43 & 18 & day & 29 & 13 & safe & 15 & 5 & child & 2060 & 185\\
\cellcolor{gray!6}{public} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{routes} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{planning} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{walk} & \cellcolor{gray!6}{1985} & \cellcolor{gray!6}{198}\\
community & 37 & 19 & physical & 28 & 11 & physical & 15 & 7 & public & 1973 & 206\\
\cellcolor{gray!6}{safe} & \cellcolor{gray!6}{34} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{health} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{healthy} & \cellcolor{gray!6}{14} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{age} & \cellcolor{gray!6}{1774} & \cellcolor{gray!6}{209}\\
benefits & 32 & 17 & inclement & 25 & 11 & traffic & 13 & 6 & urban & 1749 & 198\\

@@

\cellcolor{gray!6}{play} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{eligibility} & \cellcolor{gray!6}{24} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{support} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{different} & \cellcolor{gray!6}{1695} & \cellcolor{gray!6}{213}\\
resources & 30 & 13 & consortium & 24 & 9 & families & 13 & 5 & home & 1691 & 197\\
\cellcolor{gray!6}{healthy} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{16} & \cellcolor{gray!6}{region} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{way} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{social} & \cellcolor{gray!6}{1672} & \cellcolor{gray!6}{189}\\
routes & 27 & 13 & service & 22 & 11 & student & 12 & 5 & significant & 1644 & 206\\
\cellcolor{gray!6}{lanes} & \cellcolor{gray!6}{26} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{•} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{region} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{mobility} & \cellcolor{gray!6}{1634} & \cellcolor{gray!6}{136}\\

@@

@@

Using natural language processing techniques, we analyzed how AST is
framed in documents available to the general public on the websites of
STP stakeholder groups in Ontario. We found that AST is primarily framed
to parents as beneficial to the health and wellbeing of children and to
environmental sustainability. This was confirmed by the most common
bigrams identified in the policy corpus, as well as the topics
identified by the LDA model. The policy documents adequately reflect the
evidence that AST contributes positively to children's physical health
(see Faulkner et al., 2009; Schoeppe et al., 2015), although the
statements regarding the benefits of AST to children's school
performance and cognitive development need to be studied further to
produce stronger evidence ({\textbf{???}}). STP stakeholder groups also
communicate that increasing AST may reduce traffic near and around
schools. This presumably is communicated to alleviate parental concerns
about traffic and safety (Evers et al., 2014; Mammen et al., 2012;
Rothman et al., 2015; Wilson et al., 2018) or reduce the frequency of
risky behaviours from drivers around schools (Rothman et al., 2017).
However, the documents do not explain why declining rates of AST are a
problem for the particular community or convey any urgency to this issue
so that it attracts the attention of parents, the general public, or
policy makers. Communicating the potential outcomes of increased AST may
be persuasive arguments to motivate behaviour change, but these
documents do not appear to encourage parents or the general public to
view their behaviour as problematic or unhealthy for their children's
development. For example, parents who escort their children to school
have reported concerns about traffic volume around schools (Mammen et
al., 2012), but may not recognize that their own behaviour contributes
to the problem that is perceived to prevent their child from safely
walking or bicycling to school (Collins and Kearns, 2001).

@@

Given the range of factors that influence AST in a Canadian setting
(\emph{inter alia}, see Mammen et al., 2012; Mitra, 2013; Rothman et
al., 2018; Wilson et al., 2018), STP stakeholder groups must decide
which points of intervention that they can reasonably have some
influence towards. This would also depend on the local context to ensure
that barriers to AST as perceived by parents are addressed. It could be
that STP stakeholder groups perceive to have more control over
micro-scale elements of the built environment, like traffic calming
measures or speed limits, rather ``non-modifiable'' factors like street
density or land use mix. It would also certainly be much more difficult
for STP stakeholder groups to influence the number of trips to different
destinations that households need to make or to intervene in residential
location, which affects distance to school. A focus on changing parental
perceptions is recommended by many scholars since parents are the
``gatekeeper'' for children's mobility, but the information communicated
by STP stakeholder groups in Ontario should reflect a broader range of
factors that influence AST.

@@

There is a noticeable lack of focus on individual and interpersonal
determinants of AST in the policy documents. For example, the role of
convenience and inclement weather in shaping household travel decisions
(Buliung et al., 2011) or the age at which children become allowed to
travel by active modes or independently (Mammen et al., 2012) were not
discussed. The desire to escort children to school, which has been noted
by parents as a reason to continue driving (Westman, Friman, et al.,
2017), is also not adequately addressed by STP stakeholder groups. The
complexity of travel arrangements that must be coordinated by households
(see Buliung et al., 2021) and the dominant parenting culture to protect
children from risk ({\textbf{???}}) are likewise overlooked. STP
stakeholders may wish to emphasize to parents that older children have
greater traffic safety and cognitive abilities to navigate their own
routes to school, which could encourage parents to develop their
child(ren)'s travel skills over time. Additional attention should be
paid to the reasons why parents perceive driving to be more convenient.

@@

Although the ``policy stream'' appears to have been adequately engaged
in Ontario communities, it could be that the decline of AST has not been
sufficiently framed as ``problematic'' to warrant more widespread
awareness or solutions. If Canadian STP stakeholder groups wish to
involve more local residents in their efforts (Buttazzoni et al., 2018),
it would also be worthwhile for them to produce different materials that
communicate why this issue is important to the general public,
regardless of whether they currently have children commuting to/from
school. The ``political stream'' could also be further engaged by
working with advocacy groups who could attract more support from a
broader coalition of individuals.

@@

\leavevmode\hypertarget{ref-romeroChildrenExperiencesEnjoyment2015}{}%
Romero, V., 2015. Children's experiences: Enjoyment and fun as
additional encouragement for walking to school. Journal of Transport \&
Health 2, 230--237.
doi:\href{https://doi.org/10.1016/j.jth.2015.01.002}{10.1016/j.jth.2015.01.002}
